%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper, 11pt, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{footmisc} % enabling footnotes.

\usepackage[scale=0.75]{geometry}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\input{personalinfo}
% personalinfo.tex:
% \newcommand{\MyEmailAddress}{name.surname@whateverdomain.com}
% \newcommand{\MyPhoneNumber}{+391112223333}
% \newcommand{\MyPhoneNumberAsString}{(+39)~111~222~3333}

\firstname{Lorenzo}
\familyname{Ferrari}
% \phone[mobile]{\MyPhoneNumberAsString}
% \email{\MyEmailAddress}
\title{Curriculum Vitae}


%----------------------------------------------------------------------------------------

\begin{document}
\thispagestyle{empty}

\makecvtitle

%----------------------------------------------------------------------------------------
%   PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% \section{Personal information}
% \cvitem{}{Lorenzo Ferrari}
% \cvitem{Born in}{Trento (Italy), April 4, 2004}
% \cvitem{Email}{\href{mailto:\MyEmailAddress}{\texttt{\MyEmailAddress}}}
% \cvitem{Phone}{\href{tel:\MyPhoneNumber}{\texttt{\MyPhoneNumberAsString}}}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2023--Present}{Bachelor's degree in Mathematics}{University of Pisa.}{}{}{}
\cventry{2023--Present}{Degree in Mathematics}{Scuola Normale Superiore}{Pisa.}{}{}
\cventry{2018--23}{Secondary School}{Liceo Scientifico ``G. Galilei''}{Trento}{100/100.}{}
\cventry{2021--22}{Exchange year in Denmark}{AFS}{}{Rønne.}{} %{Between September 2021 and June 2022 I have lived in Denmark with my host family, learning to know a new culture and new amazing people.}
\cventry{2021--23}{IOI Team Selection}{National Olympiad in Informatics}{Italy and Denmark.}{}{} %{Training camps each consisting of both lessons (advanced Algorithms, Data Structures, Problem Solving techniques) and competitions.}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{2023--Present}{Member of the Scientific Staff of the Italian Olympiad in Informatics}{}{Italy.}{}{Invented, prepared and tested problems that appeared in the National Olympiad in Informatics and in later phases of the IOI team selection. In particular, I am responsible for teaching the lessons.}
\cventry{2025}{Coordination of ``Scienziate di Domani''}{Scuola Normale Superiore}{Italy.}{}{I coordinated the 2025 edition of Scienziate di Domani: an initiative for girls in high school aimed to reduce the gender gap among students in top STEM programs, such as the Corso Ordinario in Scuola Normale Superiore. I also taught Mathematics lessons.}
\cventry{2022,23}{Huawei Summer Camp}{Huawei \{Zurich, Pisa\} Research Center}{}{\{80, 36\} hours.}{Respectively (Zurich) designing approximation algorithms for real-life-like problems, (Pisa) designing and implementing a system to assign limited resources to different users.}
\cventry{2022--23}{coderfarm-it}{Associazione Promozione Programmazione Competitiva}{}{45 hours.}{I taught the \href{https://github.com/coderfarm-it/materiali/tree/main/corso-avanzato}{advanced section} of remote lessons in Competitive Programming for high school students across Italy.}
\cventry{2021--Present}{Lecturing}{}{}{}{I have delivered various lectures in Competitive Programming and Mathematics with focus on Olympiad preparation, both as voluntarily and professionally, on several additional occasions.}
\cventry{2020--21}{Voluntary work}{Trentino Solidale}{Trento.}{}{My fellow scouts and I volunteered in the food program ``Trentino Solidale'' during the whole year.}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}
\cvitem{2023--Present}{Full scholarship by Scuola Normale Superiore}{}
\subsection{Informatics}
\cventry{2024-25}{ICPC Europe Championship (EUC)}{}{}{Highest Honors}{}
\cventry{2023-24}{Southwestern Europe Regional Contest (SWERC)}{}{}{bronze medal (7th place)}{Consequent invitation to the 2024 ICPC Europe Training Camp powered by Huawei.}

\cventry{2020--22}{National Olympiad in Informatics}{}{}{one silver and two gold medals (one first place)}{}
\cventry{2022\footnotemark[1]}{International Olympiad in Informatics}{}{}{honourable mention}{}
\footnotetext[1]{I also qualified for IOI 2023, but was unable to compete due to a scheduling conflict with university entrance exams.}
\cventry{2023}{Romanian Master of Informatics}{}{}{silver medal}{}
\cventry{2023}{Balkan Olympiad in Informatics}{}{}{silver medal}{}
\cventry{2022}{Baltic Olympiad in Informatics}{}{}{bronze medal}{}
\cventry{2021,23}{National Informatics Olympiad in Teams}{}{}{one third place and one first place}{}
\cventry{2021,23}{International Informatics Olympiad in Teams}{}{}{bronze medal}{}
\subsection{Mathematics}
\cventry{2021,23}{National Olympiad in Mathematics}{}{}{one bronze medal and one silver medal}{}
\cventry{2022}{Georg Mohr-Konkurrencen (Danish Olympiad in Mathematics)}{}{}{first place}{}
\cventry{2022}{Nordic Mathematical Contest}{}{}{13th place}{}
\subsection{Miscellaneous}
\cventry{2021}{European Olympiad of Experimental Science}{}{}{first team in Italy}{}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\section{Technical skills}
\cvitem{Advanced}{\textsc{C++}, Competitive Programming}{}
\cvitem{Intermediate}{\textsc{Python}, Linux, \LaTeX, \textsc{Git}}{}
\cvitem{Basic}{Typst, \textsc{CMake}, \textsc{SQLite}}{}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}
\cvitemwithcomment{Italian}{Native speaker}{}
\cvitemwithcomment{English}{Advanced}{Cambridge CAE Grade A, 2023}
\cvitemwithcomment{Danish}{Intermediate}{Self-assessed}
\cvitemwithcomment{German}{Lower-intermediate}{Deutsches Sprachdiplom I, 2020}

%----------------------------------------------------------------------------------------
%	INTERESTS
%----------------------------------------------------------------------------------------

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\section{Interests}

\cvlistdoubleitem{People (and stories they have to tell)}{Reading}
\cvlistdoubleitem{Hiking}{Ultimate Frisbee}
\cvlistdoubleitem{Board games}{Table Football}

%----------------------------------------------------------------------------------------
%	FOOTER
%----------------------------------------------------------------------------------------

\vfill
I hereby consent to the processing of the personal data in this document under the EU Regulation 2016/679 (General Data Protection Regulation) for the sole purpose of consideration of my skills and experience for academic or professional opportunities.

\end{document}
